Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-06 Ch1_movement_rates/Ch1_Figures.Rmd
Display just the figures

```{r}
set.seed(98)

@@

# Average movement rate for this 'population'
mean(indiv_moverate$movrate)
mean(ptpl$mpm)

@@

logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
# Mean using the fit
exp(logfit$estimate[1])

# Visualize distribution and data points
vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]

@@

```{r}
# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:

mean(indiv_moverate$movrate)
# 27.94211 meters/minute

@@

# ggsave2(filename = "Ch1_movement_rates/Figures/Movement_dist_comparison_2exp.png", width = 6, height = 4, units = "in")

@@

movrate_cp_ln

@@

sim_movement(prm = movrate_cp_ln, plot.it = TRUE, return.data.frame = TRUE)
# Print the data frame with seed info
test_run <- sim_seeds(nseeds = nseeds, m.prms = movrate_cp_ln)
test_run

@@

```{r}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

@@

# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

@@

@@

fam_moverate %>%
  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
  geom_point(size = 3) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  xlim(0, 60) +
  labs(title = "Lognormal fitted to family group",
       x = "Movement rate",
       y = "Density") +
  scale_color_viridis_c() +
  theme_bw() +
  theme(legend.position = "none") -> pp_logfit

@@

```{r}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

```{r}
# This one looks at individual variation.
# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')

>>>>

```{r include=FALSE}
set.seed(98)

@@

# Average movement rate for this 'population'
# mean(indiv_moverate$movrate)
# mean(ptpl$mpm)

@@

logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")
# Mean using the fit
exp(logfit$estimate[1])
```

```{r}
# Visualize distribution and data points
vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]

@@

```{r include=FALSE}
# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:

# mean(indiv_moverate$movrate)
# 27.94211 meters/minute

@@

```{r}
# ggsave2(filename = "Ch1_movement_rates/Figures/Movement_dist_comparison_2exp.png", width = 6, height = 4, units = "in")

@@

# movrate_cp_ln

@@

#sim_movement(prm = movrate_cp_ln, plot.it = TRUE, return.data.frame = TRUE)
# Print the data frame with seed info
test_run <- sim_seeds(nseeds = nseeds, m.prms = movrate_cp_ln)
#test_run

@@

```{r include=FALSE}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

@@

# Mean using the fit
# exp(logfit_fam$estimate[1])

```{r}
# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

@@

```{r include=FALSE}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

```{r}
# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

@@

fam_moverate %>%
  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
  geom_point(size = 3) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  xlim(0, 60) +
  labs(title = "Lognormal fitted to family group",
       x = "Movement rate",
       y = "Density") +
  scale_color_viridis_c() +
  theme_bw() +
  theme(legend.position = "none") -> pp_logfit

@@

```{r include=FALSE}
# This one looks at individual variation.
# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')
